Energy and the CES production function

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
update to triPlot

<<>>=
triPlot(
  data=AllCoeffs, 
  aes(x = alpha_3, y = alpha_1, z = alpha_2, 
      fill  = nest, 
      shape = nest,
      size = CSP, alpha = CSP)) +
  facet_grid(. ~ Country) +
  scale_size_manual(values = c(5, 2)) +
  scale_alpha_manual(values = c(.2, .6)) +
  scale_shape_manual(values = 21:25)
@

>>>>

<<fig.height=3>>=
triPlot(
  data=
    AllCoeffs %>% 
    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
            Inputs = flavor), 
  aes(x = alpha_3, y = alpha_1, z = alpha_2, 
      fill  = Model, 
      shape = Model,
      size = Model, 
      color = Inputs),
  alpha = 0.6) +
  facet_grid(. ~ Country) +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
  scale_shape_manual(values = 21:25)  
@
